draft 1

### 2016-04-27 finalwriteup/draft.rmd
further work on method

---
title: "draft 1"
author: "Amy Cook"
date: "Tuesday, July 07, 2015"
output: word_document
bibliography: Library2.bib
---

@@

Timesheet Data
* percent of hours performed by each professional role for the entire project
* timespan of the entered project hours
* percent of hours performed by 'profesional' employees as opposed to 'technical'
* total cost of employee hours per project
* total cost of external subcontractors or disbursements per project
* total number of users that entered hours on each project
* mean hours per day entered on a project
* number of disciplines active in a project

Invoicing data
* total amount invoiced and renumerated per project
* mean invoice size per project
* mean invoice per client
* invoice frequency per project
* client invoice frequency

Project Data
* text analysis of project descriptions detected a list of key words that could classify projects into 16 categories. This key word analysis was done in conjunction with a company employee and the resulting classifications were reviewed.
* number of projects completed with each client and client contact

Once the three data sources were combined, further variables were engineered:
* project profit
* return per dollar for each project (how much was spent on expenses for every dollar earned?)

>>>>

---
title: "draft 1"
author: "Amy Cook"
date: "Tuesday, July 07, 2015"
output: word_document
bibliography: Library.bib
---

@@

Timesheet Data

* percent of hours performed by each professional role for the entire project
* timespan of the entered project hours
* percent of hours performed by 'profesional' employees as opposed to 'technical'
* total cost of employee hours per project
* total cost of external subcontractors or disbursements per project
* total number of users that entered hours on each project
* mean hours per day entered on a project
* number of disciplines active in a project

Invoicing data

* total amount invoiced and renumerated per project
* mean invoice size per project
* mean invoice per client
* invoice frequency per project
* client invoice frequency

Project Data

* text analysis of project descriptions detected a list of key words that could classify projects into 16 categories. This key word analysis was done in conjunction with a company employee and the resulting classifications were reviewed.
* number of projects completed with each client and client contact

Once the three data sources were combined, further variables were engineered:

* project profit
* return per dollar for each project (how much was spent on expenses for every dollar earned?)
